Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-20 Paper.tex
Minor fix () is the empty list/sequence, not the empty byte array - replaced with 0 where appropriate.

The genesis block is 13 items, and is specified thus:
\begin{equation}
\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, stateRoot, (), 2^{22}, 0, 0, 1000000, 0, 0, (), \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)
\end{equation}

Where $0_{256}$ refers to the parent hash, a 256-bit hash which is all zeroes; $0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes; $2^{22}$ refers to the difficulty; 0 refers to the timestamp (the Unix epoch); $()$ refers to the transaction trie root, extradata and the sequences of both uncles and transactions, all empty. $\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42. $\mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big)$ value refers to the hash of the uncle lists in RLP, both empty lists.

>>>>

The genesis block is 13 items, and is specified thus:
\begin{equation}
\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, stateRoot, 0, 2^{22}, 0, 0, 1000000, 0, 0, 0, \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)
\end{equation}

Where $0_{256}$ refers to the parent hash, a 256-bit hash which is all zeroes; $0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes; $2^{22}$ refers to the difficulty; 0 refers to the timestamp (the Unix epoch); the transaction trie root and extradata are both $0$, being equivalent to the empty byte array. The sequences of both uncles and transactions are empty and represented by $()$. $\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42. $\mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big)$ value refers to the hash of the uncle lists in RLP, both empty lists.
